## Sample report

This is an example of the type of report you can write in Radiant.

* You can create
* bullet lists

1. And numbered
2. lists

### Math

You can even include math if you want:

$$y_t = \\alpha + \\beta x_t + \\epsilon_t.$$

To show the output press the `Knit report` button.

### Documenting analysis results in Radiant

The report feature in Radiant should be used in conjunction with the <i title='Report results' class='fa fa-edit'></i> icons shown at the bottom of the side bar on (almost) all pages. When that icon is clicked the command used to create the ouput is copied into the editor in the _R > Report_ tab. By default Radiant will paste the code generated for the analysis you just completed at the bottom of the report (i.e., `Auto paste`). However, you can turn off that feature by selecting `Manual paste` from the dropown. With manual paste on, the code is put in the clipboard when you click a report icon and you can paste it where you want in the _R > Report_ editor window.

By clicking the `Knit report` button or pressing CTRL-return (CMD-return on Mac), the output from the analysis will be recreated. You can add text, bullets, headers, etc. around the code blocks to describe and explain the results using <a href='http://rmarkdown.rstudio.com/authoring_pandoc_markdown.html' target='_blank'>markdown</a>. You can also select part of the report you want to render.

Below is some code created in Radiant that will generate regression outputfor the _diamonds_ data. These are histograms and a scatterplot / heatmap of the price of diamonds versus carats. The colors in the plot reflect the clarity of the diamond.

```{r fig.width=7, fig.height=4}
result <- regression(dataset = 'diamonds', rvar = 'price', evar = 'carat')
summary(result)
plot(result, plots = 'hist')
```

```{r fig.width=7, fig.height=7}
visualize(dataset = 'diamonds', xvar = 'carat', yvar = 'price',
          type = 'scatter', color = 'clarity')
```

> **Put your own code here or delete this sample report and create your own**
"
